Implementation of poloidal density variation in collision operator

### 2019-03-08 doc/classical_radial_fluxes_2019-01-17.tex
Updates classical heat flux to correct for an incorrect factor 2 in the normalization. Adds a notice that this correction has been applied to the output, for automatic correction. Updates documentation to reflect these changes.

%=================================================================
\begin{document}
\section{Drift-kinetic classical transport}
These notes derive the classical transport under the same set of assumptions as in the linearized drift-kinetic equation solved by the $\delta f$-code neoclassical code \textsc{Sfincs} (and probably most other neoclassical codes).

@@

\section{SFINCS implementation}
\textsc{Sfincs} uses normalized quantities (denoted with a hat), where the normalized radial fluxes are defined in terms of the physical fluxes as
\begin{align}
  \hat{\Gamma}_a &= \frac{\bar{R}}{\bar{n}\bar{v}} \frac{1}{Z_a e} \lang B^{-2} \left(\vec{B} \times \nabla \hat{\psi}\right) \cdot \vec{R}_a \rang, \\
  \hat{Q}_a &= \frac{\bar{R}}{\bar{n}\bar{v} \bar{T}} \frac{1}{Z_a e} \lang B^{-2} \left(\vec{B} \times \nabla \hat{\psi}\right) \cdot \vec{G}_a \rang,
\end{align}
where $\hat{\psi} = \psi/(\bar{B}\hat{R}^2)$ is just a new choice of radial coordinate rather than a normalization -- see the \textsc{Sfincs} manual for more details. We also define the dimensionless parameters $\alpha = e\bar{\Phi}/\bar{T}$ and $\Delta = \frac{\sqrt{2\bar{m}\bar{T}}}{e\bar{R}\bar{B}}$, and the dimensionless collisionality $\nu_n$
\begin{align}
  \bar{\nu} &\equiv \frac{\sqrt{2}}{12 \pi^{3/2}} \frac{\bar{n} e^4 \ln \Lambda}{\epsilon_0^2 \bar{m}^{1/2} \bar{T}^{3/2}} \\
  \nu_n &\equiv \bar{\nu} \frac{\bar{R} \sqrt{\bar{m}}}{\sqrt{2\bar{T}}} =\frac{1}{12 \pi^{3/2}} \frac{\bar{n} \bar{R} e^4 \ln \Lambda}{\epsilon_0^2 \bar{T}^{2}},
\end{align}
so that
\begin{equation}
\frac{1}{\tau_{ab} n_b} = \frac{Z_a^2 Z_b^2}{\hat{m}_a^{1/2} \hat{T}_a^{3/2}} \frac{\sqrt{2} \bar{T}^{1/2}}{\bar{n} \bar{R} \bar{m}^{1/2}} \nu_n = \frac{Z_a^2 Z_b^2}{\hat{m}_a^{1/2} \hat{T}_a^{3/2}} \frac{\sqrt{2} \bar{T}^{1/2}\bar{m}^{1/2} \bar{B}}{\bar{n} \bar{R} \bar{B} \bar{m}} \nu_n = \frac{Z_a^2 Z_b^2}{\hat{m}_a^{1/2} \hat{T}_a^{3/2}} \frac{e\bar{B}}{\bar{n}\bar{m}} \Delta \nu_n.
\end{equation}
With this, the normalized particle and conductive heat-flux becomes
\begin{equation}
\begin{aligned}
  \hspace*{-10ex} \hat{\Gamma}_a =   \frac{\Delta^2 \nu_n}{2}\frac{Z_a\hat{m}_a^{1/2}}{\hat{T}_a^{3/2}}\sum_b Z_b^2 &\left[
    \lang  \hat{n}_a \hat{n}_b\frac{ |\bar{R}\nabla \hat{\psi}|^2}{\hat{B}^2} \rang M_{ab}^{00} \left(\frac{ \hat{T}_a}{Z_a}  \frac{\d \ln\eta_a}{\d \hat{\psi}} -\frac{ \hat{T}_b}{Z_b}  \frac{\d \ln\eta_b}{\d \hat{\psi}}\right) \right.\\
    &\left.+    \lang \hat{n}_a \hat{n}_b\frac{  |\bar{R}\nabla \hat{\psi}|^2}{\hat{B}^2} \hat{\Phi}_1 \rang \alpha  M_{ab}^{00} \left(\frac{\d \ln T_a}{\d \hat{\psi}} -\frac{\d \ln T_b}{\d \hat{\psi}}\right) \right.\\
   &\left. + \lang \hat{n}_a \hat{n}_b \frac{| \bar{R} \nabla \hat{\psi}|^2 }{\hat{B}^2}\rang\left(  \left(M_{ab}^{00} - M_{ab}^{01}\right)\frac{ \hat{T}_a}{Z_a}\frac{\d \ln T_a}{\d \hat{\psi}} 
    - \left(M_{ab}^{00} - \frac{\hat{m}_a \hat{T}_b}{\hat{m}_b \hat{T}_a} M_{ab}^{01}\right)\frac{ \hat{T}_b}{Z_b}\frac{\d \ln T_b}{\d \hat{\psi}}\right)\right] 
\end{aligned}
\end{equation}

\begin{equation}
\begin{aligned}
  \hspace*{-10ex} \hat{q}_a =  -\frac{\Delta^2 \nu_n}{2} \frac{Z_a\hat{m}_a^{1/2}}{\hat{T}_a^{1/2}} \sum_b Z_b^2 &\left[
    \lang \hat{n}_a \hat{n}_b\frac{|\bar{R}\nabla \hat{\psi}|^2}{\hat{B}^2 } \rang M_{ab}^{01}\left(\frac{\hat{T}_a}{Z_a}  \frac{\d \ln\eta_a}{\d \hat{\psi}} - \frac{\hat{T}_b}{Z_b}\frac{\d \ln\eta_b}{\d \hat{\psi}}\right) \right.\\
    &\left.+\lang \hat{n}_a \hat{n}_b\frac{|\bar{R}\nabla \hat{\psi}|^2}{\hat{B}^2 }  \hat{\Phi}_1 \rang \alpha M_{ab}^{01} \left(\frac{\d \ln T_a}{\d \hat{\psi}}-\frac{\d \ln T_b}{\d \hat{\psi}}\right) \right.\\
    &\left.+ \lang \hat{n}_a \hat{n}_b\frac{|\bar{R}\nabla \hat{\psi}|^2}{\hat{B}^2 } \rang \left(\left(M_{ab}^{01} - M_{ab}^{11}\right)\frac{ \hat{T}_a}{Z_a} \frac{\d \ln T_a}{\d \hat{\psi}}
    - \left(M_{ab}^{01} + N_{ab}^{11}\right)\frac{\hat{T}_b}{Z_b}\frac{\d \ln T_b}{\d \hat{\psi}}\right) \right].
\end{aligned}
\end{equation}
Finally, using $\hat{n}_a = \hat{\eta}_a \e^{-Z_a \alpha \hat{\Phi}_1/\hat{T}_a}$, we get
\begin{equation}
\hat{n}_a\hat{n}_b = \hat{\eta}_a \hat{\eta}_b \exp{\left(-\alpha\hat{\Phi}_1\left[\frac{Z_a}{\hat{T}_a} + \frac{Z_b}{\hat{T}_b}\right]\right)},
\end{equation}
where $\hat{\eta}$ is the ``density'' in \textsc{Sfincs}, which is a flux-function. In the code, we define
\begin{align}
  G_{ab}^{(1)} =& \lang \exp{\left(-\alpha\hat{\Phi}_1\left[\frac{Z_a}{\hat{T}_a} + \frac{Z_b}{\hat{T}_b}\right]\right)}\frac{|\bar{R}\nabla \hat{\psi}|^2}{\hat{B}^2 } \rang \\
  G_{ab}^{(2)} =& \lang \exp{\left(-\alpha\hat{\Phi}_1\left[\frac{Z_a}{\hat{T}_a} + \frac{Z_b}{\hat{T}_b}\right]\right)}\frac{|\bar{R}\nabla \hat{\psi}|^2}{\hat{B}^2 } \hat{\Phi}_1 \rang,
\end{align}
so that
\begin{equation}
\begin{aligned}
  \hspace*{-10ex} \hat{\Gamma}_a =   \frac{\Delta^2 \nu_n}{2}\frac{Z_a\hat{m}_a^{1/2} \hat{\eta}_a}{\hat{T}_a^{3/2}}\sum_b Z_b^2 \hat{\eta}_b&\left[
    G_{ab}^{(1)} M_{ab}^{00} \left(\frac{ \hat{T}_a}{Z_a}  \frac{\d \ln\eta_a}{\d \hat{\psi}} -\frac{ \hat{T}_b}{Z_b}  \frac{\d \ln\eta_b}{\d \hat{\psi}}\right) \right.\\
    &\left.+    G_{ab}^{(2)} \alpha  M_{ab}^{00} \left(\frac{\d \ln T_a}{\d \hat{\psi}} -\frac{\d \ln T_b}{\d \hat{\psi}}\right) \right.\\
   &\left. +G_{ab}^{(1)}\left(  \left(M_{ab}^{00} - M_{ab}^{01}\right)\frac{ \hat{T}_a}{Z_a}\frac{\d \ln T_a}{\d \hat{\psi}} 
    - \left(M_{ab}^{00} - \frac{\hat{m}_a \hat{T}_b}{\hat{m}_b \hat{T}_a} M_{ab}^{01}\right)\frac{ \hat{T}_b}{Z_b}\frac{\d \ln T_b}{\d \hat{\psi}}\right)\right],
\end{aligned}
\end{equation}

\begin{equation}
\begin{aligned}
  \hspace*{-10ex} \hat{q}_a =  -\frac{\Delta^2 \nu_n}{2} \frac{Z_a\hat{m}_a^{1/2} \hat{\eta}_a}{\hat{T}_a^{1/2}} \sum_b Z_b^2 \hat{\eta}_b &\left[
    G_{ab}^{(1)}  M_{ab}^{01}\left(\frac{\hat{T}_a}{Z_a}  \frac{\d \ln\eta_a}{\d \hat{\psi}} - \frac{\hat{T}_b}{Z_b}\frac{\d \ln\eta_b}{\d \hat{\psi}}\right) \right.\\
    &\left.+G_{ab}^{(2)} \alpha M_{ab}^{01} \left(\frac{\d \ln T_a}{\d \hat{\psi}}-\frac{\d \ln T_b}{\d \hat{\psi}}\right) \right.\\
    &\left.+ G_{ab}^{(1)} \left(\left(M_{ab}^{01} - M_{ab}^{11}\right)\frac{ \hat{T}_a}{Z_a} \frac{\d \ln T_a}{\d \hat{\psi}}
    - \left(M_{ab}^{01} + N_{ab}^{11}\right)\frac{\hat{T}_b}{Z_b}\frac{\d \ln T_b}{\d \hat{\psi}}\right) \right],
\end{aligned}
\end{equation}
and
\begin{equation}
\hat{Q}_a = \hat{q}_a + \frac{5}{2} \hat{T}_a \hat{\Gamma}_a. 
\end{equation}

>>>>

%=================================================================
\begin{document}
\textcolor{red}{Update 2019-03-08: the normalized heat flux was a factor 2 too high due to using the wrong normalization. This has been corrected.}

\section{Drift-kinetic classical transport}
These notes derive the classical transport under the same set of assumptions as in the linearized drift-kinetic equation solved by the $\delta f$-code neoclassical code \textsc{Sfincs} (and probably most other neoclassical codes).

@@

\section{SFINCS implementation}
\textsc{Sfincs} uses normalized quantities (denoted with a hat), where the normalized radial fluxes are defined in terms of the physical fluxes as
\begin{align}
  \hat{\Gamma}_a &= \frac{\bar{R}}{\bar{n}\bar{v}} \frac{1}{Z_a e} \lang B^{-2} \left(\vec{B} \times \nabla \hat{\psi}\right) \cdot \vec{R}_a \rang, \\
  \hat{Q}_a &= \frac{\bar{R}}{\bar{n}\bar{m}\bar{v}^3} \frac{1}{Z_a e} \lang B^{-2} \left(\vec{B} \times \nabla \hat{\psi}\right) \cdot \vec{G}_a \rang,
\end{align}
where $\hat{\psi} = \psi/(\bar{B}\hat{R}^2)$ is just a new choice of radial coordinate rather than a normalization -- see the \textsc{Sfincs} manual for more details. We also define the dimensionless parameters $\alpha = e\bar{\Phi}/\bar{T}$ and $\Delta = \frac{\sqrt{2\bar{m}\bar{T}}}{e\bar{R}\bar{B}}$, and the dimensionless collisionality $\nu_n$
\begin{align}
  \bar{\nu} &\equiv \frac{\sqrt{2}}{12 \pi^{3/2}} \frac{\bar{n} e^4 \ln \Lambda}{\epsilon_0^2 \bar{m}^{1/2} \bar{T}^{3/2}} \\
  \nu_n &\equiv \bar{\nu} \frac{\bar{R} \sqrt{\bar{m}}}{\sqrt{2\bar{T}}} =\frac{1}{12 \pi^{3/2}} \frac{\bar{n} \bar{R} e^4 \ln \Lambda}{\epsilon_0^2 \bar{T}^{2}},
\end{align}
so that
\begin{equation}
\frac{1}{\tau_{ab} n_b} = \frac{Z_a^2 Z_b^2}{\hat{m}_a^{1/2} \hat{T}_a^{3/2}} \frac{\sqrt{2} \bar{T}^{1/2}}{\bar{n} \bar{R} \bar{m}^{1/2}} \nu_n = \frac{Z_a^2 Z_b^2}{\hat{m}_a^{1/2} \hat{T}_a^{3/2}} \frac{\sqrt{2} \bar{T}^{1/2}\bar{m}^{1/2} \bar{B}}{\bar{n} \bar{R} \bar{B} \bar{m}} \nu_n = \frac{Z_a^2 Z_b^2}{\hat{m}_a^{1/2} \hat{T}_a^{3/2}} \frac{e\bar{B}}{\bar{n}\bar{m}} \Delta \nu_n.
\end{equation}
With this, the normalized particle and conductive heat-flux becomes
\begin{equation}
\begin{aligned}
  \hspace*{-10ex} \hat{\Gamma}_a =   \frac{\Delta^2 \nu_n}{2}\frac{Z_a\hat{m}_a^{1/2}}{\hat{T}_a^{3/2}}\sum_b Z_b^2 &\left[
    \lang  \hat{n}_a \hat{n}_b\frac{ |\bar{R}\nabla \hat{\psi}|^2}{\hat{B}^2} \rang M_{ab}^{00} \left(\frac{ \hat{T}_a}{Z_a}  \frac{\d \ln\eta_a}{\d \hat{\psi}} -\frac{ \hat{T}_b}{Z_b}  \frac{\d \ln\eta_b}{\d \hat{\psi}}\right) \right.\\
    &\left.+    \lang \hat{n}_a \hat{n}_b\frac{  |\bar{R}\nabla \hat{\psi}|^2}{\hat{B}^2} \hat{\Phi}_1 \rang \alpha  M_{ab}^{00} \left(\frac{\d \ln T_a}{\d \hat{\psi}} -\frac{\d \ln T_b}{\d \hat{\psi}}\right) \right.\\
   &\left. + \lang \hat{n}_a \hat{n}_b \frac{| \bar{R} \nabla \hat{\psi}|^2 }{\hat{B}^2}\rang\left(  \left(M_{ab}^{00} - M_{ab}^{01}\right)\frac{ \hat{T}_a}{Z_a}\frac{\d \ln T_a}{\d \hat{\psi}} 
    - \left(M_{ab}^{00} - \frac{\hat{m}_a \hat{T}_b}{\hat{m}_b \hat{T}_a} M_{ab}^{01}\right)\frac{ \hat{T}_b}{Z_b}\frac{\d \ln T_b}{\d \hat{\psi}}\right)\right] 
\end{aligned}
\end{equation}

\begin{equation}
\begin{aligned}
  \hspace*{-10ex} \hat{q}_a =  -\frac{\Delta^2 \nu_n}{\textcolor{red}{4}} \frac{Z_a\hat{m}_a^{1/2}}{\hat{T}_a^{1/2}} \sum_b Z_b^2 &\left[
    \lang \hat{n}_a \hat{n}_b\frac{|\bar{R}\nabla \hat{\psi}|^2}{\hat{B}^2 } \rang M_{ab}^{01}\left(\frac{\hat{T}_a}{Z_a}  \frac{\d \ln\eta_a}{\d \hat{\psi}} - \frac{\hat{T}_b}{Z_b}\frac{\d \ln\eta_b}{\d \hat{\psi}}\right) \right.\\
    &\left.+\lang \hat{n}_a \hat{n}_b\frac{|\bar{R}\nabla \hat{\psi}|^2}{\hat{B}^2 }  \hat{\Phi}_1 \rang \alpha M_{ab}^{01} \left(\frac{\d \ln T_a}{\d \hat{\psi}}-\frac{\d \ln T_b}{\d \hat{\psi}}\right) \right.\\
    &\left.+ \lang \hat{n}_a \hat{n}_b\frac{|\bar{R}\nabla \hat{\psi}|^2}{\hat{B}^2 } \rang \left(\left(M_{ab}^{01} - M_{ab}^{11}\right)\frac{ \hat{T}_a}{Z_a} \frac{\d \ln T_a}{\d \hat{\psi}}
    - \left(M_{ab}^{01} + N_{ab}^{11}\right)\frac{\hat{T}_b}{Z_b}\frac{\d \ln T_b}{\d \hat{\psi}}\right) \right].
\end{aligned}
\end{equation}
Finally, using $\hat{n}_a = \hat{\eta}_a \e^{-Z_a \alpha \hat{\Phi}_1/\hat{T}_a}$, we get
\begin{equation}
\hat{n}_a\hat{n}_b = \hat{\eta}_a \hat{\eta}_b \exp{\left(-\alpha\hat{\Phi}_1\left[\frac{Z_a}{\hat{T}_a} + \frac{Z_b}{\hat{T}_b}\right]\right)},
\end{equation}
where $\hat{\eta}$ is the ``density'' in \textsc{Sfincs}, which is a flux-function. In the code, we define
\begin{align}
  G_{ab}^{(1)} =& \lang \exp{\left(-\alpha\hat{\Phi}_1\left[\frac{Z_a}{\hat{T}_a} + \frac{Z_b}{\hat{T}_b}\right]\right)}\frac{|\bar{R}\nabla \hat{\psi}|^2}{\hat{B}^2 } \rang \\
  G_{ab}^{(2)} =& \lang \exp{\left(-\alpha\hat{\Phi}_1\left[\frac{Z_a}{\hat{T}_a} + \frac{Z_b}{\hat{T}_b}\right]\right)}\frac{|\bar{R}\nabla \hat{\psi}|^2}{\hat{B}^2 } \hat{\Phi}_1 \rang,
\end{align}
so that
\begin{equation}
\begin{aligned}
  \hspace*{-10ex} \hat{\Gamma}_a =   \frac{\Delta^2 \nu_n}{2}\frac{Z_a\hat{m}_a^{1/2} \hat{\eta}_a}{\hat{T}_a^{3/2}}\sum_b Z_b^2 \hat{\eta}_b&\left[
    G_{ab}^{(1)} M_{ab}^{00} \left(\frac{ \hat{T}_a}{Z_a}  \frac{\d \ln\eta_a}{\d \hat{\psi}} -\frac{ \hat{T}_b}{Z_b}  \frac{\d \ln\eta_b}{\d \hat{\psi}}\right) \right.\\
    &\left.+    G_{ab}^{(2)} \alpha  M_{ab}^{00} \left(\frac{\d \ln T_a}{\d \hat{\psi}} -\frac{\d \ln T_b}{\d \hat{\psi}}\right) \right.\\
   &\left. +G_{ab}^{(1)}\left(  \left(M_{ab}^{00} - M_{ab}^{01}\right)\frac{ \hat{T}_a}{Z_a}\frac{\d \ln T_a}{\d \hat{\psi}} 
    - \left(M_{ab}^{00} - \frac{\hat{m}_a \hat{T}_b}{\hat{m}_b \hat{T}_a} M_{ab}^{01}\right)\frac{ \hat{T}_b}{Z_b}\frac{\d \ln T_b}{\d \hat{\psi}}\right)\right],
\end{aligned}
\end{equation}

\begin{equation}
\begin{aligned}
  \hspace*{-10ex} \hat{q}_a =  -\frac{\Delta^2 \nu_n}{\textcolor{red}{4}} \frac{Z_a\hat{m}_a^{1/2} \hat{\eta}_a}{\hat{T}_a^{1/2}} \sum_b Z_b^2 \hat{\eta}_b &\left[
    G_{ab}^{(1)}  M_{ab}^{01}\left(\frac{\hat{T}_a}{Z_a}  \frac{\d \ln\eta_a}{\d \hat{\psi}} - \frac{\hat{T}_b}{Z_b}\frac{\d \ln\eta_b}{\d \hat{\psi}}\right) \right.\\
    &\left.+G_{ab}^{(2)} \alpha M_{ab}^{01} \left(\frac{\d \ln T_a}{\d \hat{\psi}}-\frac{\d \ln T_b}{\d \hat{\psi}}\right) \right.\\
    &\left.+ G_{ab}^{(1)} \left(\left(M_{ab}^{01} - M_{ab}^{11}\right)\frac{ \hat{T}_a}{Z_a} \frac{\d \ln T_a}{\d \hat{\psi}}
    - \left(M_{ab}^{01} + N_{ab}^{11}\right)\frac{\hat{T}_b}{Z_b}\frac{\d \ln T_b}{\d \hat{\psi}}\right) \right],
\end{aligned}
\end{equation}
and
\begin{equation}
\hat{Q}_a = \hat{q}_a + \frac{5}{\textcolor{red}{4}} \hat{T}_a \hat{\Gamma}_a. 
\end{equation}

### 2019-03-08 doc/manual/version3/outputParameters.tex
Updates classical heat flux to correct for an incorrect factor 2 in the normalization. Adds a notice that this correction has been applied to the output, for automatic correction. Updates documentation to reflect these changes.

\outputparamWithUnderscore{classicalHeatFlux\_\textcolor{magenta}{Y}}
{classicalHeatFlux_Y}
{\parlink{Nspecies}~$\times$~\parlink{NIterations} matrix of reals}
{\parlink{RHSMode} == 1 and \parlink{solveSystem} == \true}
{\todo{Can Stefan update the text so it is correct?}\newline
$\displaystyle \text{\ttfamily classicalHeatFlux\_\textcolor{magenta}{Y}} = \frac{\bar{R}}{\bar{n} \bar{v}} \frac{1}{Z_s e} \left\langle \frac{\vect{B} \times \nabla \textcolor{magenta}{Y}}{B^2} \cdot \vect{R}_s \right\rangle$ for all plasma species. $\displaystyle \vect{R}_s = m_s \sum_a \int d^3v \, \vect{v} C_s \left[f_s, f_a\right]$ is the friction force acting on the species. The final result is in the last index corresponding to the last nonlinear iteration.\newline
For different options of $\textcolor{magenta}{Y}$ see flux-surface labels (section~\ref{sec:radialCoordinates}).}

@@

\outputparamWithUnderscore{classicalHeatFluxNoPhi1\_\textcolor{magenta}{Y}}
{classicalHeatFluxNoPhi1_Y}
{\parlink{Nspecies} array of reals}
{\parlink{RHSMode} == 1}
{\todo{Can Stefan update the text so it is correct?}\newline
$\displaystyle \text{\ttfamily classicalHeatFluxNoPhi1\_\textcolor{magenta}{Y}} = \frac{\bar{R}}{\bar{n} \bar{v}} \frac{1}{Z_s e} \left\langle \frac{\vect{B} \times \nabla \textcolor{magenta}{Y}}{B^2} \cdot \vect{R}_{s,\,\mathrm{w/o}\,\Phi_1} \right\rangle$ for all plasma species. $\displaystyle \vect{R}_{s,\,\mathrm{w/o}\,\Phi_1} = m_s \sum_a \int d^3v \, \vect{v} C_s \left[f_{s,\,\mathrm{w/o}\,\Phi_1}, f_{a,\,\mathrm{w/o}\,\Phi_1}\right]$ is the friction force acting on the species, where the impact of $\Phi_1$ is neglected.\newline
For different options of $\textcolor{magenta}{Y}$ see flux-surface labels (section~\ref{sec:radialCoordinates}).}

>>>>

\outputparamWithUnderscore{classicalHeatFlux\_\textcolor{magenta}{Y}}
{classicalHeatFlux_Y}
{\parlink{Nspecies}~$\times$~\parlink{NIterations} matrix of reals}
{\parlink{RHSMode} == 1 and \parlink{solveSystem} == \true}
{$\displaystyle \text{\ttfamily classicalHeatFlux\_\textcolor{magenta}{Y}} = \frac{\bar{R}}{\bar{n} \bar{v}^3 \bar{m}} \frac{1}{Z_s e} \left\langle \frac{\vect{B} \times \nabla \textcolor{magenta}{Y}}{B^2} \cdot \vect{G}_s \right\rangle$ for all plasma species. $\displaystyle \vect{G}_s = \frac{m_s^2}{2}\sum_a \int d^3v \, \vect{v} v^2 C_s \left[f_s, f_a\right]$ is the energy-weighted friction force acting on the species. The final result is in the last index corresponding to the last nonlinear iteration.\newline
For different options of $\textcolor{magenta}{Y}$ see flux-surface labels (section~\ref{sec:radialCoordinates}).}

@@

\outputparamWithUnderscore{classicalHeatFluxNoPhi1\_\textcolor{magenta}{Y}}
{classicalHeatFluxNoPhi1_Y}
{\parlink{Nspecies} array of reals}
{\parlink{RHSMode} == 1}
{$\displaystyle \text{\ttfamily classicalHeatFluxNoPhi1\_\textcolor{magenta}{Y}} = \frac{\bar{R}}{\bar{n} \bar{v}^3\bar{m}} \frac{1}{Z_s e} \left\langle \frac{\vect{B} \times \nabla \textcolor{magenta}{Y}}{B^2} \cdot \vect{G}_{s,\,\mathrm{w/o}\,\Phi_1} \right\rangle$ for all plasma species.  $\displaystyle \vect{G}_{s,\,\mathrm{w/o}\,\Phi_1} = \frac{m_s^2}{2}\sum_a \int d^3v \, \vect{v} v^2 C_s \left[f_{s,\,\mathrm{w/o}\,\Phi_1}, f_{a,\,\mathrm{w/o}\,\Phi_1}\right]$ is the energy-weighted friction force acting on the species, where the impact of $\Phi_1$ is neglected.\newline
For different options of $\textcolor{magenta}{Y}$ see flux-surface labels (section~\ref{sec:radialCoordinates}).}
